\documentclass[12pt, a4paper]{article}
\usepackage{a4wide}
\usepackage{DejaVuSans}
\usepackage{listings}
\usepackage{courier}
\usepackage{amssymb}
\usepackage{amsmath}
\renewcommand*\familydefault{\sfdefault} 
\lstset{basicstyle=\ttfamily}
\begin{document}
\section*{Classes}
\begin{enumerate}
    \item Create a class called \lstinline{Motor} that represents the motor, fuel tank and transmission of a car. It should contain the private attributes \lstinline[breaklines=true]{gearRatio (float), maximumFuelLevel (float, in liters), currentFuelLevel (float, in liters), currentSpeed (float, in km/h), fuelEfficiency (float)} where \lstinline{fuelEfficiency(float)} represents the fuel consumption of liters per 100km.
    \item Create constructors: One without any arguments, one with all, more as you see fit. Which default values do you deem reasonable? Why?
    \item Create the public functions \lstinline[breaklines=true]{getCarSpeed, getFuelLevel, getFuelQuota, refill, setEngineSpeed, getGearRatio, drive(int)} where \lstinline{drive(int)} gets a distance driven (in km) and updates the fuel level accordingly.
    \item Use classifiers (such as \lstinline[breaklines=true]{const, volatile, mutable}) as you see fit. Justify your decisions.
\end{enumerate}
\section*{Inheritance}
\begin{enumerate}
    \item Rename the class to \lstinline{ElectroMotor} and create a class \lstinline{DieselMotor} and an interface \lstinline{Motor}. Move as many attributes and functions from \lstinline{ElectroMotor} to \lstinline{Motor} as you see fit. Replicate all other attributes and functions in the newly created class \lstinline{DieselMotor}.
    \item Use classifiers (such as \lstinline{const, volatile, mutable, virtual}) as you see fit. Justify your decisions.
    \item How is the interface \lstinline{Motor} distinguished from the classes \lstinline{ElectroMotor} and \lstinline{DieselMotor}?
\end{enumerate}
\section*{Polymorphism}
\begin{enumerate}
    \item Modify the interface \lstinline{Motor} so that every class extending it is forced to implement an own version of the function \lstinline{getGearRatio} without having to implement the functions \lstinline{getCarSpeed, drive}. Which classifier is necessary for this?
    \item Create a class \lstinline{Gear} that represents one of the gears a transmission of a diesel-powered car can be in. It should only contain the private attribute \lstinline{gearRatio (float)} and public function \lstinline{getGearRatio()}. Modify the class \lstinline{DieselMotor} to accept a positive number of gears with different gear ratios and store them (sorted) in a suitable attribute in a container provided by the standard library.
    \item Create the functions \lstinline{increaseGear(), decreaseGear(), setGear(unsigned int)} for the class \lstinline{DieselMotor} to switch between its gears. Modify the function \lstinline{getGearRatio} accordingly.
\end{enumerate}
\end{document}
